Growth Resilience

### 2017-06-21 analysis/analysis_resilience_bai.Rmd
update plots two events

  # interaction 
  ph_i <- lsmeans(mymodel, pairwise ~ disturb_year:site, adjust = "tukey")

@@

  # Return objects
  cat('\n### Event ###\n')
  print(ph_event)
  print(cld_event)
  cat('\n### Clu pop ###\n')
  print(ph_site)
  print(cld_site)
  cat('\n### Event:Clu pop ###\n')
  print(ph_i)
  return(list(aux_ph_site, aux_ph_event, aux_ph_i))
}
```

@@

>>>>

  # interaction 
  ph_i <- lsmeans(mymodel, pairwise ~ disturb_year:site, adjust = "tukey")
  cld_i <- cld(ph_i, alpha   = 0.01, 
                 Letters = letters, 
                 adjust  = "tukey")

@@

  # Return objects
  cat('\n### Event ###\n')
  print(ph_event)
  print(cld_event)
  cat('\n### Clu pop ###\n')
  print(ph_site)
  print(cld_site)
  cat('\n### Event:Clu pop ###\n')
  print(ph_i)
  return(list(aux_ph_site, aux_ph_event, aux_ph_i, cld_site, cld_event, cld_i))
}
```

@@

```{r}
# Interactions plot all  
means_site <- postH_rc[[4]] %>% mutate(var = 'rc') %>% 
  bind_rows(postH_rt[[4]] %>% mutate(var = 'rt')) %>% 
  bind_rows(postH_rs[[4]] %>% mutate(var = 'rs')) %>% 
  bind_rows(postH_rrs[[4]] %>% mutate(var = 'rrs')) %>% 
  rename(letras = .group)

means_disturb <- postH_rc[[5]] %>% mutate(var = 'rc') %>% 
  bind_rows(postH_rt[[5]] %>% mutate(var = 'rt')) %>% 
  bind_rows(postH_rs[[5]] %>% mutate(var = 'rs')) %>% 
  bind_rows(postH_rrs[[5]] %>% mutate(var = 'rrs')) %>% 
  rename(letras = .group)

means_distub_site <- postH_rc[[6]] %>% mutate(var = 'rc') %>% 
  bind_rows(postH_rt[[6]] %>% mutate(var = 'rt')) %>% 
  bind_rows(postH_rs[[6]] %>% mutate(var = 'rs')) %>% 
  bind_rows(postH_rrs[[6]] %>% mutate(var = 'rrs')) %>% 
  rename(letras = .group)

dodge <- position_dodge(width = 0.3)
micolor <- '#455883'
```

```{r}
means_site %>%  
  ggplot(aes(x=site, y=lsmean)) + 
  geom_errorbar(aes(ymin=lsmean - SE, ymax=lsmean + SE), 
                color=micolor, size=.5, width=.15, position = dodge) +
  geom_point(colour=micolor, 
             size=3, position = dodge) +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15)

```{r}
means_disturb %>%  
  ggplot(aes(x=disturb_year, y=lsmean)) + 
  geom_errorbar(aes(ymin=lsmean - SE, ymax=lsmean + SE), 
                color=micolor, size=.5, width=.15, position = dodge) +
  geom_point(colour=micolor, 
             size=3, position = dodge) +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15)
```

```{r}
means_distub_site %>%  
  ggplot(aes(x=site, y=lsmean, group=disturb_year, colour=disturb_year)) + 
  geom_errorbar(aes(ymin=lsmean - SE, ymax=lsmean + SE), 
                size=.5, width=.15) + 
  geom_point(aes(shape=disturb_year), size=3) + 
  geom_line() +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15)
```
